%-------------------------
% Resume in Latex
% Author: Stanley Ho
%
%
% Original source : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/stanleyycho/}{\Large Stanley Ho}} & Email : \href{mailto:stanleyho1988@gmail.com}{stanleyho1988@gmail.com}\\
  \href{https://www.linkedin.com/in/stanleyycho/}{https://www.linkedin.com/in/stanleyycho/} \\
\end{tabular*}

%--------SUMMARY OF QUALIFICATIONS------------
\section{Summary}
  \resumeSubHeadingListStart
    \item {Demonstrated hands-on programming skills and knowledge in software development and imaging processing}
    \item {Strong problem-solving and analytical skills with the ability to work on various projects}
    \item {Possess strong commitment to team environment and good communication skill}
  \resumeSubHeadingListEnd
  
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C++, C, Matlab, JavaScript, Java, Shell script, Python}
      
      \textbf{Technologies}{: Intel IPP, OpenCV, AngularJS, Jenkins, Apache httpd}
    }
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Roche Tissue Diagnostics}{Mountain View, CA}
      {Software Engineer}{Nov 2013 - Present}
      \resumeItemListStart
        \resumeItem{Segmentation}
          {Contributed to image segmentation algorithm, which classifies tissue regions with deep learning approach, and integrated to imaging platform.}
        \resumeItem{Image server}
          {Implemented giga-pixel microscopy image server in C++ using Apache httpd server to improve performance, stability and streamline workflow.}
        \resumeItem{Platform}
          {Contributed to developing front-end and back-end of web-based image analysis platform, which includes image viewer and analysis algorithms. The viewer is written with AngularJS in JavaScript. The platform has digitized tissue diagnostics and accelerated pharmaceutical development process.}
        \resumeItem{Image server}
          {Developed multi-channel of image server serving giga-pixel microscopy images in Java.}
        \resumeItem{Segmentation}
          {Worked with scientist to prototype semi-automatic interactive segmentation tool for real-time tissue segmentation in Matlab. Implemented it in C++ and integrated to image analysis platform.}
        \resumeItem{Dev Environment}
          {Improved building, unit testing and continuous integration tools to streamline software development process.}
        \resumeItem{Framework}
          {Contributed to developing features, maintained framework, unit testing and documentation of image analysis SDK in both C++ and Matlab.}
      \resumeItemListEnd

    

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
%\section{Projects}
%  \resumeSubHeadingListStart
%    \resumeSubItem{QuantSoftware Toolkit}
%      {Open source python library for financial data analysis and machine learning for finance.}
%    \resumeSubItem{Github Visualization}
%      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%    \resumeSubItem{Recommendation System}
%      {Music and Movie recommender systems using collaborative filtering on public datasets.}
%    \resumeSubItem{Mac Setup}
%      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%  \resumeSubHeadingListEnd

%


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Santa Barbara}{Santa Barbara, CA}
      {Master of Science, Electrical and Computer Engineering;}{Jun. 2013}
    %\resumeSubheading
    %{Emphasis on Signal Processing, Minor Computer Engineering} {}
    \resumeItemListStart
        \resumeItem{Project}
          {Improved 3D image registration routine by aligning 2D image sequences written in C.}
        \resumeItem{Coursework}
          {Advanced Computer Vision, Digital Speech Processing, Pattern Recognition.}
     \resumeItemListEnd
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
