%-------------------------
% Resume in Latex
% Author: Stanley Ho
%
%
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Set table in itemized list  
\newlist{deflist}{description}{2}
\setlist[deflist]{labelwidth=2cm,leftmargin=!}

%-------------------------
% Custom commands
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
    \vspace{-7pt}
}

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSummary}[1]{
  \vspace{11pt}
  	\small {#1 \vspace{-6pt}}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Stanley Ho}} & Mountain View, CA \\
   \href{https://www.linkedin.com/in/stanleyycho/}{https://www.linkedin.com/in/stanleyycho/} & Email : \href{mailto:stanleyho1988@gmail.com}{stanleyho0826@gmail.com}\\
 \href{https://stanleyho.info/}{https://stanleyho.info/} & Phone: +1-805-570-2560\\
  %\href{https://github.com/stanleyycho}{https://github.com/stanleyycho}\\
\end{tabular*}

%--------SUMMARY OF QUALIFICATIONS------------
\section{Summary}
	\hspace{3ex}{Software professional with 7+ years' experience in design and developing robust software. Equipped with hands-on programming and problem-solving skills. Adapted to fast-paced environment and excelled in cross-functional teamwork. Possess passion for solving challenging problems and knowledge in computer vision/imaging processing. }
  
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item[]{
      \begin{deflist}
        \item[\textbf{Languages}]{C++, C, Python, JavaScript, Matlab, Shell Script, Java, SQL} \vspace{-7pt}
      \end{deflist}
    }
    \item[]{
      \begin{deflist}
        \item[\textbf{Technologies}]{Intel IPP, OpenCV, Boost, Angular, React, Docker, Linux, Jenkins, Nodejs} \vspace{-5pt}
      \end{deflist}
    }
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Deepmap}{Palo Alto, CA}
      {Software Engineer}{May 2019 - Present}
      \resumeSummary 
      {Contributed to on-board software for building high-definition maps for autonomous vehicles.}
      \resumeItemListStart
        \resumeItem {Data Collection}
        {Developed data collection coverage analysis feature in C++, which scales up mapping capacity, and mentored interns in the project.}
        \resumeItem {Map Management}
        {Contributed to design and implementation on-board software and UI for map management.}
        \resumeItem {Benchmark}
        {Built benchmark framework in Python for on-board map change detection service.}
      \resumeItemListEnd
    \resumeSubheading
      {Roche Tissue Diagnostics}{Santa Clara, CA}
      {Senior Software Engineer}{Nov 2013 - May 2019}
      \resumeSummary 
      {Built cloud-based images analysis platform for Pathology. The platform has revolutionized tissue diagnostics and accelerated pharmaceutical development process.}
      \resumeItemListStart
        \resumeItem {Image Server}
          {Implemented high resolution microscopy image HTTP server in C++. Improved scalability, response time and throughput by 50\%.}
        \resumeItem {Machine Learning Pipeline}
          {Built cloud-based image analysis pipeline, which serves as data management and pipeline for data labeling and machine learning model training.}
        \resumeItem {Detection}
          {Contributed to developing cell detection algorithm in deep learning. Integrated and productized it to image analysis platform.}
        \resumeItem {Framework}
          {Contributed to developing features of image processing/computer vision library in C++.}
        \resumeItem {Segmentation}
          {Implemented semi-automatic interactive segmentation algorithm and tool for real-time tissue segmentation in Matlab and in C++.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CERTIFICATION-----------------
\section{Certifications}
  \resumeSubHeadingListStart
    %\item[]{
    %  \textbf{Nvidia Deep Learning Institute} \href{https://courses.nvidia.com/certificates/2ccc14d1bf9746a1ab360a48b94e4af3}{Fundamentals of Deep Learning for Computer Vision}
    %}
    \item[]{
      \begin{deflist}
      	\item[\textbf{Coursera}]\href{https://www.coursera.org/account/accomplishments/specialization/G8TS8APA3NK6}{Deep Learning Specialization}, \href{https://www.coursera.org/account/accomplishments/specialization/ACYMK9U2ARYZ}{TensorFlow in Practice Specialization}
      \end{deflist}
    }
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Santa Barbara}{Santa Barbara, CA}
      {Master of Science, Electrical and Computer Engineering}{Sep 2011 - Jun 2013}
    %\resumeSubheading
    %{Emphasis on Signal Processing, Minor Computer Engineering} {}
    \resumeSubheading
      {National Chiao Tung University}{Hsinchu, Taiwan}
      {Bachelor of Science, Industrial Engineering}{Sep 2006 - Jun 2010}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
